Parallel Deduplication with Batch Scheduling for Collocated Virtual Machine Backup in the Cloud

### 2014-01-07 batchdedup/scheduling.tex
updates to histogram

Figure~\ref{sizeDistribution} shows the size distribution of VMs for a dataset from Alibaba containing
about 3000VMs. The largest VM size is to a few terabytes while  the smallest VMs only have a few gigabytes of data.
The percentage of changes from last backup is also show in the graph and 
it shows that the change is fairly uniform for large VMs also. Namely when scheduling all VM backup tasks
in one round in a synchronized manner, and the average backup time per VM is fairly large.

@@

To determine how evenly distributed VM sizes are, we obtained statistical data
for 22 Aliyun clusters. The clusters in our dataset all have a very long tail distribution,
Though local minima exist in the histogram and the range of VM sizes varies. Other production clusters
may have different distributions, but our findings justify our architecture for a multi-round algorithm.
A representative histogram for one of the clusters is shown in Fig.~\ref{fig:hist-1}.

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}
      \begin{axis}[
              ybar interval,
      ]
          \addplot+[hist={bins=10}] table[y=AY41G] {figures/cluster_distributions.txt};
      \end{axis}
  \end{tikzpicture}
  \caption{Histogram of average data sizes for a real cluster. TODO:reformat graph, I just wanted to get the data into the paper}
  \label{fig:hist-1}
\end{figure}

>>>>

%Figure~\ref{sizeDistribution} shows the size distribution of VMs for a dataset from Alibaba containing
%about 3000VMs. The largest VM size is to a few terabytes while  the smallest VMs only have a few gigabytes of data.
%The percentage of changes from last backup is also show in the graph and 
%it shows that the change is fairly uniform for large VMs also. Namely when scheduling all VM backup tasks
%in one round in a synchronized manner, and the average backup time per VM is fairly large.

@@

To determine how evenly distributed VM sizes are, we obtained statistical data
for 22 Aliyun clusters. The clusters in our dataset all have a very long tail distribution,
Though local minima exist in the histogram and the range of VM sizes varies. Other production clusters
may have different distributions, but our findings justify our architecture for a multi-round algorithm.
A representative histogram for one of the clusters is shown in Fig.~\ref{fig:hist-1}. You can see that the range of sizes is very large (the smallest group of 100 VMs has an average size of ~15GB, while the largest has an average size of over 700GB). It is that fact that VM sizes vary greatly that makes the scheduling of VMs to rounds important.

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}
      \begin{axis}[
              ybar interval,
              xlabel=Avg VM Size in Group (GB),
              ylabel=Number of Groups,
              xticklabel={\pgfmathparse{(\tick*1)}\num[round-mode=places, round-precision=0]{\pgfmathresult}}
      ]
          \addplot+[hist={bins=10}] table[y=AY41G] {figures/cluster_distributions.txt};
      \end{axis}
  \end{tikzpicture}
  \caption{Histogram of average data sizes for a real cluster. TODO:adjust this using the new spreadsheets}
  \label{fig:hist-1}
\end{figure}
